\begin{thebibliography}{00}
%\bibitem{b2} T. Rosen, W.-S. Ong, and J. Upton, “ECE570 Final Paper,” Mar. 1996.
%\bibitem{b3} Asjad, Salahuddin \& Sildnes, Anders. (2016). Comparing Hardware Prefetching Schemes on an L2 Cache.


% The book
\bibitem{Book}Hennessy, J.L.; Patterson, D.A. Computer Organization and Design, 2nd ed. San Francisco: Morgan Kaufmann Publishers, 1997.

% chen and baer on RPT
\bibitem{Prefetch}T.-F. Chen and J.-L. Baer, “Effective hardware-based data prefetching
for high-performance processors,” Computers, IEEE Transactions on,
vol. 44, pp. 609–623, May 1995.

% RPT prefetching
\bibitem{RPT}D. Kim, “Extended data cache prefetching using a reference prediction table,” Ph.D. dissertation, 1997, aAI3114245.

% Grannes Jarhe and Natvig on DCPT
\bibitem{grannaes}Grannaes, Marius \& Jahre, Magnus \& Natvig, Lasse. (2011). Storage efficient hardware prefetching using delta correlating prediction tables. Journal of Instruction-Level Parallelism. 13. 1-16.

% Sequential prefetching


  
% Prefetching
\bibitem{prefetching} N. Honarmand, Class Lecture, Topic: "Memory Prefetching" Department of Computer Science, Stony Brook University, Stony Brook, New York, Spring, 2015.

% The image "RPT Layout"
\bibitem{RPTimage}
  S. VanderWiel and D. J. Lilja, "A Survey of Data Prefetching Techniques", 1999
% nesbit et al on DC/PC prefetching
\bibitem{PCDC}K. J. Nesbit and J. E. Smith, “Data cache prefetching using a global
history buffer,” High-Performance Computer Architecture, International
Symposium on, vol. 0, p. 96, 2004.

%NTNU M5 manual
\bibitem{M5}NTNU, M5 simulator system TDT4260 Computer Architecture User documentation, 
Trondheim, 2017.

% CPU 2000 benchmark suite
\bibitem{SPEC2000}SPEC CPU2000: Read Me First. [Online]. Available: https://www.spec.org/cpu2000/docs/readme1st.html. [Accessed: 18-Mar-2020].

% Markov
\bibitem{Markov}D. Joseph and D. Grunwald, “Prefetching using markov predictors,”
SIGARCH Comput. Archit. News, vol. 25, no. 2, pp. 252–263, May
1997.


%[#] A. Author, "Document title," Webpage name, Source/production information, Date of internet publication. [Format]. Available: internet address. [Accessed: Date of access].


\end{thebibliography}